Kindly Bent to Free Us

### 2019-11-13 kindly/motivation.tex
short intro

@@

The functional resource-passing style demonstrated for channels in
\cref{sec:session-linearity} becomes tedious when manipulating mutable
resources like buffers or connection pools.
%
To make linearity easier to use with an imperative programming style, we rely on
the notion of borrowing \cite{DBLP:conf/popl/BoylandR05}.

>>>>

\lang{} is amenable to a functional resource-passing style as it is
common in functional encodings of session types (e.g.,
\cite{DBLP:journals/jfp/Padovani17}; see also
\cref{sec:session-linearity} in the supplement). But it really shines 
when manipulating mutable resources like buffers or connection pools
using an imperative programming style. 
%
To support this usage pattern of linearity, we rely on
the notion of borrowing \cite{DBLP:conf/popl/BoylandR05}.

@@
